---
title: "Data: JXB"
date: "`r Sys.Date()`"
chunk_output_type: console
html-math-method: katex
number-sections: true
toc: true
toc-expand: 3
toc-depth: 3
toc-location: left
crossref:
  eq-prefix: Eq.
format:
 html:
  embed-resources: true
---

```{r setup, include=FALSE,echo=F,message=FALSE}
# knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
pacman::p_load(ggplot2,dplyr,ggridges,tidyr,purrr,lubridate,webr,scales,flextable,kableExtra,ggtern)
round_scale <- function (vec) 
{
    purrr::map_chr(vec, ~{
        if (is.na(.x) | abs(.x) < 1e-04) {
            formatC(.x, digits = 1, format = "e")
        }
        else if (abs(.x) < 0.001) {
            as.character(round(.x, 4))
        }
        else if (abs(.x) >= 0.001 & abs(.x) < 0.01) {
            as.character(round(.x, 3))
        }
        else if (abs(.x) >= 0.01 & abs(.x) < 1) {
            as.character(round(.x, 2))
        }
        else if (abs(.x) >= 1) {
            as.character(round(.x, 1))
        }
    })
}


view_df<- function (x) {
  x <- as.data.frame(x)
  purrr::map_dfr(1:ncol(x), ~{
    ue <- unique(x[, .x])
    if (length(ue) < 5) {
      if (is.numeric(ue)) {
        ue <- round_scale(ue)
      }
      content <- paste(sort(ue), collapse = ",")
    }
    else {
      if (all(is.na(ue))) {
        content <- "NA"
      }
      else if (is.numeric(na.omit(ue)) | all(grepl("^[0-9]+$", 
                                                   na.omit(ue)))) {
        ue <- round_scale(ue)
        if (any(is.na(ue))) {
          content <- paste0(paste(range(as.numeric(na.omit(ue))), 
                                  collapse = "~"), " include NA")
        }
        else {
          content <- paste(range(as.numeric(ue)), collapse = "~")
        }
      }
      else {
        content <- paste0("Levels number:", length(ue))
      }
    }
    data.frame(colnam = names(x)[.x], info = content)
  })
}

view_group <- function (dat, g_vec, t_vec = NULL) 
{
  if (is.null(t_vec)) {
    t_vec <- setdiff(names(dat), g_vec)
  }
  res <- Reduce(function(x, y) dplyr::left_join(x, y, by = "colnam"), 
                purrr::map(dplyr::group_split(dplyr::group_by(dplyr::select(dat, 
                                                                            all_of(c(g_vec, t_vec))), across(all_of(g_vec)))), 
                           ~{
                           view_df(.x)
                           }))
  res <- data.frame(t(res))
  names(res) <- res[1, ]
  res <- res[-1, ]
  row.names(res) <- NULL
  return(res)
}


unit<- xlsx::read.xlsx("metadata/Unit.xlsx",sheetIndex = 1) %>% 
  mutate(unit=case_when(is.na(unit)~" ",
                        grepl("\\#",unit)~gsub("\\#","Nbr.",unit),
                        T~unit),
         
         xlabel=case_when(unit==" "~trait,
                          T~paste0(trait,"\n(",unit,")")))

complete_dat <- read.csv2("output/BRIWECS_data_publication.csv") %>% 
  mutate(across(c(Sowing_date,BBCH59:Protein_yield),as.numeric),
         Environment = paste(Location, Year, sep = "_")) %>% 
  tidyr::separate(Treatment,into=c("Nitrogen","Fungicide","Water_availability"))

long <- complete_dat%>% 
  tidyr::pivot_longer(BBCH59:Protein_yield,
                      names_to="trait",values_to = "Trait") %>% 
  filter(!is.na(Trait)) 
trt.col <- c("#46A120","#004400","#D4D46A","#F1EB00")
names(trt.col) <- c("HN.NF","HN.WF","LN.NF","LN.WF")
traittbl <- long %>%
  left_join(unit ,by='trait')%>%
  view_group(.,"trait",c('Full.name',"sample.source","Trait","unit")) %>% 
  arrange(sample.source,trait) %>% 
  relocate(Full.name,sample.source) %>% 
  mutate(sample.source=gsub("biomass ","",sample.source)) %>% 
  rename("trait full name"="Full.name","column name"="trait",
         "trait source"="sample.source","trait range"="Trait") 

illu  <-  complete_dat %>% 
  group_by(BRISONr, Environment) %>% 
  summarize(across(c(Sowing_date,BBCH59:Protein_yield),function(x) mean(x, na.rm = TRUE))) %>% 
  ungroup() %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) 

tr.vec <- c("Seedyield","Seedyield_bio","Biomass_bio",
            "Harvest_Index_bio","TGW","TGW_bio","Spike_number_bio","Plantheight_bio")
phen.vec <- c("Emergence_date","BBCH59","BBCH87")
path.vec <- c("Stripe_rust","Powdery_mildew","Leaf_rust","Septoria","DTR","Fusarium")
yq.vec <- c("Sedimentation","Falling_number","Crude_protein","Protein_yield")
section_nam<- list("Agronomic traits","Yield quality","Phenology","Pathogens")
tr_list <- list(tr.vec,yq.vec,phen.vec,path.vec)

distri_plot<- function(complete_dat,tr){
  ggplot(complete_dat) +
    aes(x = .data[[tr]], y = Environment, fill = interaction(Nitrogen,Fungicide)) +
    theme_classic() +
    ggh4x::facet_nested(~Water_availability,nest_line = TRUE)+
    theme(legend.position = "bottom",strip.background = element_blank()) +
    geom_density_ridges(   
      alpha = 0.75,
      jittered_points = TRUE,
      position = "raincloud",
      point_size = 0.05,
      point_alpha = 0.2,
      scale=.8) +
    scale_fill_manual(values=trt.col) +
    scale_y_discrete(drop=FALSE) +
    xlab(with(unit,xlabel[match(tr,trait)]))+
    ylab("Location x Year")
}
cor_plot <- function(illu,tr){
  illu_cor <- illu%>% 
    dplyr::select(all_of(c(tr,"Environment","BRISONr"))) %>% 
    tidyr::pivot_wider(names_from = Environment, values_from = tr) %>%
    dplyr::select(-BRISONr) %>%
    dplyr::select(order(colnames(.))) %>% 
    cor(., use = "pairwise.complete.obs")
  ggcorrplot::ggcorrplot(illu_cor) +
    ggtitle(tr) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45,hjust=1.2,vjust=1.2)) +
    paletteer::scale_fill_paletteer_c(palette = "scico::bam", limits = c(-1, 1)) +
    xlab("") +
    ylab("")
}

#weather_import
weather_dat <- list.files(path = "data/weather",
                          pattern="*.csv",
                          full.names = T) %>%
  purrr::map_df(~read.csv2(.)) %>% 
  mutate(Date=lubridate::as_date(Date))

#weather_transform
season_join <- tidyr::expand_grid(Year = 2015:2020,
                                  Date = seq(from = lubridate::as_date("2014-09-01"),
                                             to = lubridate::as_date("2015-08-31"), by = 1)) %>% 
  mutate(Month = lubridate::month(Date),
         Date = ifelse(Month <= 8, `year<-`(Date, Year), `year<-`(Date, Year - 1)),
         Date = as_date(Date)) %>% 
  dplyr::select(-Month)

sowing_date <- complete_dat %>% 
  dplyr::select(Location, Year, Sowing_date) %>% 
  mutate(Date = as_date(paste(Year - 1, "01", "01", sep = "-")),
         Sowing_date = Date + Sowing_date) %>% 
  dplyr::select(Location, Year, Sowing_date) %>% 
  group_by(Location, Year) %>% 
  summarize(Sowing_date = mean(Sowing_date, na.rm = TRUE)) %>% 
  suppressMessages() %>% 
  ungroup()

weather_dat <- weather_dat %>% 
  left_join(season_join,"Date") %>% 
  left_join(sowing_date,by=c("Location","Year")) %>% 
  mutate(Month = month(Date)) %>% 
  filter(!is.na(Sowing_date),
         Month != 7,
         Month != 8,
         Date > Sowing_date)

pacman::p_load(dplyr,VennDiagram,purrr,readr,scales)
df <- read.csv("metadata/BRIWECs_cultivar_info.csv")
colr <- c('#188392','#EEAE24','#EE3324')

colra <- map_chr(colr,~alpha(.x,.3))

p <- venn.diagram(
  x = list(
    df %>% filter(breeding_progress==T) %>% .$BRISONr%>%  unique(), 
    df %>% filter(phaseI==T) %>% .$BRISONr%>%  unique(),
    df %>% filter(phaseII==T) %>%.$BRISONr %>%  unique()),
  category.names = c( "breeding\nprogress" ,"PhaseI","PhaseII"),
  filename = 'figure/culitvar_venn.png',
  output = TRUE ,
  imagetype="png" ,
  height = 600 , 
  width =  600 , 
  resolution = 660,
  compression = "lzw",
  lwd = 1,
  col=colr,
  fill = colra,
  cex = 0.5,
  fontfamily = "sans",
  cat.cex = 0.3,
  cat.default.pos = "outer",
  # cat.pos = c(-27, 27, 135),
  # cat.dist = c(0.055, 0.055, 0.085),
  cat.fontfamily = "sans",
  cat.col = colr
)
```



## Hightlights

::: callout-tip
```{r data_summary, warning=FALSE,echo=FALSE, message=FALSE}
#| output: asis
cat(
  sprintf(
    "## %s traits from 8 genotypes across 3 years, 1 locations and 8 managements",nrow(long)),
  sep = "\n"
) 
```
:::

::: panel-tabset
## smaall field dataset

```{r,warning=FALSE,echo=FALSE, message=FALSE}
#| label: fig-pie
first.ring <- c("Genotype","Locations","Year","Management") 
second.ring <- list(c("8\nwinter wheat\ncultivars"," "," "),
                    c("1\nGerman\nlocations","soil properties","experimental\ndesigns"),
                    c(" ","climatic\ndata","sowing\ndate"),
                    c("fungicide\napplication","water\navailability","nitrogen\nfertilization"))
repid <- purrr::map_dbl(second.ring,~{
  length(.x)
})
pheno <- purrr::map2(first.ring,repid,~{
  rep(.x,each=.y)
}) %>% unlist()

tr <- "overview"

td <- data.frame(phenotype=pheno,factor1=second.ring %>% unlist()) %>% 
  group_by(phenotype) %>% 
  mutate(n=n()) %>% ungroup()

PieDonut(td, aes(phenotype, factor1, count=n),
         explode = c(1,2,3,4),r0 = .5,
         addDonutLabel = TRUE,
         showRatioDonut = F, labelposition = 0.2,
         showRatioPie = F)
```


## 8 Managements

Management comprises of three treatments: total nitrogen, application time and water availability.

-   Nitrogen fertilizer treatment includes two application levels: high (HN: 220 kg N ha^-1^) and low (LN: 110 kg N ha^-1^), both include soil mineral nitrogen (0–90 cm) measured in early spring.

-   application time  contains two application levels: split (S) or combined (C).

-   sowing date has two levels: early (E) and late (L)

In total, there are 9 managements, while it is incomplete and depends on the location and years (@fig-managements, @tbl-managements).

```{r managements, echo=FALSE,warnings=F}
#| output: asis

```

## 24 agronomic and physiological traits

```{r number_of_observations, echo=FALSE, warning=FALSE}
#| output: asis
#| 
cat(
  sprintf("Total: %sK observations (removed outliers)", format(round(nrow(long)/1000, 1), dec=",")),
  sep = "\n"
) 

fig2 <- 
  suppressWarnings(
  long %>%left_join(unit,"trait")%>% 
  group_by(trait,sample.source) %>% summarise(n=n(),.groups = "drop") %>% 
  group_by(sample.source) %>% 
  mutate(trait = forcats::fct_reorder(trait, n)) %>%
  ggplot( aes(x=trait, y=n)) +
  geom_segment( aes(xend=trait, yend=0)) +
  geom_point( size=4, color="orange") +
  coord_flip() +
  ggh4x::facet_nested(sample.source~.,
                      nest_line=T, 
                      switch = "y",# place strip to bottom
                      scales = "free_y",space ="free_y"
                      # independent = "y"
  )+
  ggtitle(sprintf("total number of observation: %s",nrow(long)))+
  xlab("")+ylab("number of observations")+
  ggrepel::geom_text_repel(aes(label=n),
                           size=2.7,
                           hjust=0,
                           box.padding = -.1,
                           point.padding = 0,
                           nudge_y=0,
                           # nudge_x=0,
                           direction="x"
  )+
  scale_y_continuous(
    labels =label_number(scale_cut = cut_short_scale()),
    limits=c(0,37000)
  )+
  ggplot2::theme_test() +
  ggplot2::theme(axis.text.x = element_text(size = 9, 
                                            vjust = -1), 
                 axis.text.y = element_text(size = 9, 
                                            margin = margin(r = 4)),
                 axis.title = element_text(size = 9.2, face = "bold"), 
                 axis.title.y = element_text(margin = margin(r = 15), 
                                             vjust = -1),
                 axis.title.x = element_text(margin = margin(b = 3), 
                                             vjust = -4), 
                 axis.ticks = element_line(size = 0.6, color = "black"), 
                 axis.ticks.length = unit(0.2, "cm"), 
                 strip.text.x = element_text(size = 8, face = "bold"), 
                 strip.text.y = element_text(size = 8, 
                                             face = "bold"),
                 strip.background = element_blank(), 
                 panel.border = element_rect(colour = ifelse(is.null(frame), 
                                                             NA, "black"), 
                                             fill = NA, size = 0.6), 
                 axis.line = element_line(colour = "black", size = 0.6), 
                 legend.title = element_text(size = 8, face = "bold"), 
                 legend.text = element_text(size = 8,                                                                            face = "bold"), 
                 plot.margin = margin(t = 15, r = 10, 
                                      b = 10, l = 1, unit = "pt"), 
                 legend.background = element_rect(fill = NA), 
                 plot.background = element_rect(fill = "transparent"),
                 plot.title = element_text(size=10),
                 strip.placement = "outside"))

cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  sprintf("#| fig-cap: %s-datapoint", tr),
  sprintf("#| label: fig-%s-datapoint", tr),
  "suppressWarnings(suppressMessages(print(fig2)))",
  "```"
)))  
```
:::

## Experimental designs

::: panel-tabset
```{r experimental_design,echo=FALSE,warning=FALSE,message=FALSE}
#| output: asis

data <- read.csv2("output/BRIWECS_data_publication.csv") %>% 
  mutate(across(BBCH59:Protein_yield,as.numeric),
         phase=case_when(Year<2018~"Phase I",
                         T~"Phase II") %>%
           factor(.,levels=c("Phase II","Phase I"))) %>% 
  tidyr::pivot_longer(BBCH59:Protein_yield,names_to = "trait",values_to = "Trait")
data_list <- data %>% 
  group_by(Year) %>% 
  group_split() %>% 
  .[!map_lgl(.,~{all(is.na(.x$Trait))})] %>% 
  .[!map_lgl(.,~{length(which(!is.na(.x$Trait)))==1})] %>% 
  map(.,~{
    .x %>% 
      select(Year,Location,Treatment,Row,Column,phase) %>% 
      distinct() %>% 
      tidyr::separate(Treatment,into=c("Nitrogen","Fungicide","Water_availability")) %>% 
      suppressWarnings() %>% 
      mutate(across(c(Row,Column),as.integer)) %>% 
      dplyr::filter(!is.na(Row),!is.na(Column))
  })

plot_fun<- function(i){
  df <- data_list[[i]]
  df%>%
    ggplot(aes(Row,Column,color=interaction(Nitrogen,Fungicide)))+
    geom_point(size=.8)+
    scale_shape_manual(values=c(1,16))+
    theme_classic()+
    theme(legend.position="bottom",
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          strip.text=element_text(size=8),
          
          strip.background = element_blank())+
    # scale_color_brewer(palette = "Set1") +
    scale_color_manual(values=trt.col)+
    ggh4x::facet_nested(phase+Year~Water_availability+Location,nest_line = T,
                        scales="free_x",
                        space = "free_x",
                        switch = "y"
    )+
    guides(color = guide_legend(override.aes = list(size = 5))) 
}

for(i in 1:length(data_list)){ #
  tr <- data_list[[i]]$Year[1]
  cat(
    sprintf(
      "### `%s` ",tr),
    sep = "\n"
  ) 
  expp <- plot_fun(i)
  cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
    "```{r}",
    "#| echo: false",
    sprintf("#| fig-cap: %s-exp", tr),
    sprintf("#| label: fig-%s-ep", tr),
    "#| fig.asp: .8",
    "suppressWarnings(suppressMessages(print(expp)))",
    "```"
  )))
}
```
:::

## 24 Traits

```{r,echo=F}
#| tbl-cap: "Trait names, sources, ranges and units" 
#| label: tbl-trait-range-table
traittbl%>%
  kbl() %>%
  kable_classic_2(full_width = F, position = "float_right")
```

## Ranges of traits

```{r range_of_traits, warning=FALSE, message=FALSE}
#| echo: false
#| output: asis
for (i in 1:length(section_nam)) { #
  cat(
    sprintf("### %s",section_nam[[i]]),
    sep='\n')
  
  trvec <-  tr_list[[i]] 
  for (tr in trvec) {
    cat(
      sprintf(
        "#### `%s` ",tr),
      sep = "\n"
    ) 
    dp <- distri_plot(complete_dat,tr) %>% suppressWarnings() %>% suppressMessages()
    if(tr=="Emergence_date"){
      dp <- dp+xlab("days of year")
    }
    cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
      "```{r}",
      "#| echo: false",
      sprintf("#| fig-cap: %s-distribution", tr),
      sprintf("#| label: fig-%s-dp", tr),
      "#| fig.asp: 1.2",
      "suppressWarnings(suppressMessages(print(dp)))",
      "```"
    )))
    
    if(!tr%in%c("Emergence_date",path.vec)){
      cp <- cor_plot(illu,tr) %>%  suppressWarnings() %>% suppressMessages()
      cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
        "```{r}",
        "#| echo: false",
        sprintf("#| fig-cap: %s-correlation", tr),
        sprintf("#| label: fig-%s-cp", tr),
        "#| fig.asp: 1.2",
        "cp",
        "```"
      )))
    }
    if (tr=="Seedyield_bio"){
      cpp <-  suppressMessages(
        ggplot(illu) + 
          aes(x = Seedyield*10, y = Seedyield_bio) + 
          ggtitle("Comparison Combine Harvest and Hand Harvest") +
          facet_wrap(~Environment, ncol = 5) +
          theme_minimal() +
          geom_abline(intercept = 0, slope = 1) +
          geom_point(shape = 21, colour = "white", fill = "grey40", stroke = 0.2) +
          geom_smooth(method = "lm", se = FALSE, colour = "orangered2") +
          ggpmisc::stat_poly_eq(aes(label =  paste(..rr.label.., sep = "~~~~")), 
                                parse = TRUE, geom = "text_npc", formula = y~x, size = 4) +
          coord_equal()+
          xlab("Seedyield")+
          NULL
      )
      cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
        "```{r}",
        "#| echo: false",
        sprintf("#| fig-cap: correlations between whole plot and 50 cm cut", tr),
        sprintf("#| label: fig-%s-cpp", tr),
        "#| fig.asp: 1.6",
        "suppressWarnings(suppressMessages(print(cpp)))",
        "```"
      )))
    }
  }
}
```

```{r range_of_traits_2,echo=FALSE,warning=FALSE,message=FALSE}
#| output: asis
tr <- "Sowing_date"
cat(
  sprintf(
    "### %s ", tr),sep="\n")

dp <-ggplot(complete_dat) +
  aes(x = Sowing_date, y = Environment, fill = interaction(Nitrogen,Fungicide)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_density_ridges(alpha = 0.75,
                      jittered_points = TRUE,
                      position = "raincloud",
                      point_size = 0.05,
                      point_alpha = 0.2,
                      scale = 0) +
  scale_fill_manual(values=trt.col) +
  scale_x_continuous(limits = c(250, 350))+
  xlab("days of years") 

cat(sep = "\n", knitr::knit_child(quiet = TRUE, text = c(
  "```{r}",
  "#| echo: false",
  sprintf("#| fig-cap: %s-distribution", tr),
  sprintf("#| label: fig-%s-dp", tr),
  "#| fig.asp: 1.2",
  "suppressWarnings(suppressMessages(print(dp)))",
  "```"
)))
```

## Climate data

```{r,echo=FALSE,warning=FALSE,message=FALSE}
#| label: fig-precipitation
#Cumulated_Weather_Precipitation
wsub <- weather_dat %>% 
  filter(Month < 8,
         Month > 2) %>% 
  group_by(Location, Year) %>% 
  arrange(Date) %>% 
  mutate(Precipitation.Cumsum_mm_d = cumsum(Precipitation_mm_d),
         Date_max = max(Date)) %>% 
  ungroup() %>% 
  mutate(Date_Fake = ifelse(Month <= 8, `year<-`(Date, 2015), `year<-`(Date, 2014)),
         Date_Fake = as_date(Date_Fake),
         Environment = paste(Location, Year, sep = "_"),
         label = ifelse(Date == Date_max, Environment, NA)) %>% 
  group_by(Date_Fake) %>% 
  mutate(Precipitation.Cumsum.Mean_mm_d = mean(Precipitation.Cumsum_mm_d, na.rm = TRUE)) %>% 
  ungroup()

plot_1 <- wsub %>% 
  select(Date_Fake,Environment,
         label,Precipitation.Cumsum_mm_d,Precipitation.Cumsum.Mean_mm_d) %>% 
  # filter(!is.na(Precipitation.Cumsum_mm_d),
  #        !is.na(Precipitation.Cumsum.Mean_mm_d)) %>% 
  ggplot() + 
  aes(x = Date_Fake,
      y = Precipitation.Cumsum_mm_d - Precipitation.Cumsum.Mean_mm_d, 
      colour = Environment) +
  ggtitle("March to harvest") +
  theme_classic() +
  theme(plot.margin = margin(0.1, 3, 0.1, 0.1, "cm")) +
  geom_hline(yintercept = 0, colour = "grey", size = 2) +
  geom_line() +
  ggrepel::geom_text_repel(aes(label = label),
                           direction = "y",
                           hjust = 0,
                           size = 3,
                           segment.alpha = .5,
                           nudge_x = 10,
                           segment.linetype = "dotted",
                           xlim = c(-Inf, Inf),
                           max.overlaps = 20) +
  labs(x = "Date",
       y = quote(Precipitation[Cumsum]~Mean~Deviation~~'['*mm*']')) +
  scale_colour_viridis_d(option = "turbo") +
  guides(colour = "none") +
  # scale_x_date(limits = c(ymd("2014-06-30"), ymd("2015-06-30"))) +
  coord_cartesian(
    xlim = c(ymd("2015-03-01"), ymd("2015-06-30")),
    ylim = c(-200, 200),
    clip = "off",
    expand = 0
  ) 

plot_1%>% suppressWarnings()

```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
#| label: fig-globalrad
#Cumulated_Weather_GlobRad
wsub <- weather_dat %>% 
  filter(Month < 8,
         Month > 2) %>% 
  group_by(Location, Year) %>% 
  arrange(Date) %>% 
  mutate(Global.Radiation.CumSum_MJ_m2_d = cumsum(Global.Radiation_MJ_m2_d),
         Date_max = max(Date)) %>% 
  ungroup() %>% 
  mutate(Date_Fake = ifelse(Month <= 8, `year<-`(Date, 2015), `year<-`(Date, 2014)),
         Date_Fake = as_date(Date_Fake),
         Environment = paste(Location, Year, sep = "_"),
         label = ifelse(Date == Date_max, Environment, NA)) %>% 
  group_by(Date_Fake) %>% 
  mutate(Global.Radiation.CumSum.Mean_MJ_m2_d = mean(Global.Radiation.CumSum_MJ_m2_d, na.rm = TRUE)) %>% 
  ungroup()

plot_1 <- 
  ggplot(wsub) + 
  aes(x = Date_Fake,
      y = Global.Radiation.CumSum_MJ_m2_d - Global.Radiation.CumSum.Mean_MJ_m2_d,
      colour = Environment) +
  ggtitle("March to harvest") +
  theme_classic() +
  theme(plot.margin = margin(0.1, 3, 0.1, 0.1, "cm")) +
  geom_hline(yintercept = 0, colour = "grey", size = 2) +
  geom_line() +
  ggrepel::geom_text_repel(aes(label = label),
                           direction = "y",
                           hjust = 0,
                           size = 3,
                           segment.alpha = .5,
                           nudge_x = 10,
                           segment.linetype = "dotted",
                           xlim = c(-Inf, Inf),
                           max.overlaps = 20) +
  labs(x = "Date",
       y = quote(Global~Radiation[Cumsum]~Mean~Deviation~~'['*MJ%.%m^-2*']')) +
  scale_colour_viridis_d(option = "turbo") +
  guides(colour = FALSE) +
  coord_cartesian(
    xlim = c(ymd("2015-03-01"), ymd("2015-06-30")),
    ylim = c(-280, 280),
    clip = "off",
    expand = 0
  ) 

plot_1 %>% suppressWarnings()
```
